Using traffic analysis to identify The Second Generation Onion Router

### 2011-05-15 thesis/results.tex
Explain the adaboost and j4.8 algorithms

j4.8 is a free Java version of the C4.5 algorithm, a classifier which builds a
decision tree using the concept of information entropy
\parencite{Quinlan:1993:CPM:152181}. This algorithm was chosen because of it's
successful use in earlier traffic classification publications.

@@

\subsection{Adaboost}

AdaBoost or Adaptive Boosting

>>>>

j4.8 is a Java version of the C4.5 classification algorithm, which has a
permissive open source license and is available in the Weka software suite. It
builds a decision tree using the concept of information entropy
\parencite{Quinlan:1993:CPM:152181}, creating decision branches for features of
a set of data that display the most uncertainty. This algorithm was chosen
because of it's successful use in earlier traffic classification publications.

@@

\subsection{AdaBoost}

Adaptive Boosting is a technique of combining various weak classifiers to
create a strong classifier \parencite{Schapire:1999uq}, the AdaBoost algorithm.
It has been used successfully in several traffic classification applications
\parencite{Alshammari:2009p7474,Haffner:2005p3822,Mohd:2009p6484} and purports
to not suffer from the problem of over-fitting.
